---
title: "Developing Data Products"
subtitle: "Week 4 Assignment"
author: "I. Diaz"
date: "4/25/2020"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, result='hide', warning=FALSE, message=FALSE)
```

## Developing Data Products

<font size = "3">
The purpose of this assignment is to create a Shiny application using the shiny library in RStudio, This presentation is going to explain how I made it, briefly.

I hope you like this presentation.

</font>

## What you'll find?

- About Data.
- ui.R explained.
- server.R decodified

## Code Description

<font size = "3">
I've used data from https://opendata.ecdc.europa.eu/covid19 to get updated COVID-19 info. 
The data is in the csv file called "covid-19.csv".

```{r data, result="hide", warning=FALSE, message=FALSE}
#Loading Libraries
library(tidyverse)
library(plotly)
library(leaflet)
library(rgdal)
library(RColorBrewer)
library(shiny)
library(DT)

#importing data
dataset <- read.csv("covid-19.csv")

```

Data looks like this:

```{r data_show, echo=TRUE}
head(dataset)
```

</font>

## ui.R

<font size = "3">
The first part of the file defines the layout of the dashboard. `tabsetPanel` creates the tabs up in the page, and every `tabPanel` define each content. The first panel contains the data, so the user can explore it. The second one contains an interactive figure, and the third one contains a map. 

```{r ui_r, echo=TRUE, results='hide'}
shinyUI(fluidPage(
    tabsetPanel(tabPanel("All Data", titlePanel("Updated Covid-19 Dataset"),
                         fluidRow(column(DT::dataTableOutput("RawData"), width = 12))),
                tabPanel("Figure", titlePanel("Top Countries with Covid-19"),
                         sidebarLayout(sidebarPanel(numericInput("cbarras", "Bar Quantity", 
                                          value = 10, 1, 15, 1)), 
                          mainPanel(plotOutput("plot1")))),
                tabPanel("Map", titlePanel("Covid-19 Worldwide Map"),
                         mainPanel(plotlyOutput("plot2")))
                )))
```

</font>

## setup.R

<font size = "3">
In `output$RawData` are instructions to display a interactive table to show all Covid-19 updated dataset used to construct the chart and map. `output$plot1` render the bar chart that is able to select the number of bars the user wants to see. `output$plot2` render the map in plotly generated in the last assingment.

</font>

## Code

<font size = "3">

```{r setup_r, echo=TRUE, results='hide'}
shinyServer(function(input, output) {
    output$RawData <- DT::renderDataTable(
        DT::datatable({dataset}, options = list(lengthMenu = list(c(5,15,-1), c('5', '15', 'All')), pageLength = 15), filter = "top", selection = 'multiple', style = 'bootstrap'))
    
    output$plot1 <- renderPlot({
        countries <- head(dataset[c('countriesAndTerritories', 'cases')], input$cbarras)
        countries %>% ggplot(aes(x = reorder(countriesAndTerritories, -cases), y = cases))+
            geom_bar(stat = "identity", fill = 'lightblue') + theme_minimal() + xlab("Country") + ylab("Nº of Cases")})
    
    output$plot2 <- renderPlotly({
        fig <- dataset
        fig <- fig %>%
            plot_ly(lat = ~lat, lon = ~lng, size = ~cases, sizes = c(10, 100), marker = list(color = 'blue', opacity = 0.5, sizemode = 'diameter'), type = 'scattermapbox', hovertext = paste(fig$countriesAndTerritories, '\n Confirmed Cases: ', fig$cases)) 
        fig <- fig %>%
            layout(title = 'How Covid-19 is today',mapbox = list(style = 'open-street-map', zoom =2.5, center = list(lon = -70, lat = -33)), autosize = FALSE, width = 1200, height = 800)
        fig})
})
```

</font>

## THANK YOU 